Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-07-29 summary.Rmd
fixed typo

```{r clust_err_sim, fig.cap = 'IQR clustering error using Algorithm 1 (red) compared against subspace clustering (blue) for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  labs(y = 'clustering error', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 1')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 1')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1')
```

>>>>

```{r clust_err_sim, fig.cap = 'IQR clustering error using Algorithm 1 (red) compared against subspace clustering (blue) for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = 'clustering error', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 1')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 1')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1')
```
